---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
```

# IMSB

<!-- badges: start -->
`r badger::badge_custom("version", badger::ver_devel(), color = "FFA70B")`
<!-- badges: end -->

The goal of the `imsb` package is to provide all the materials (e.g., data, utility functions) needed for the [IMSB course](https://www.barelysignificant.com/IMSB2022/).

## Installation

You can install the development version of `imsb` from GitHub with:

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github(repo = "lnalborczyk/IMSB2022/_imsb", dependencies = TRUE)
```

## Usage

Checking the packages install.

```{r example1, eval = FALSE}
library(imsb)
check_install()
```

Opening the slides of the first course in browser.

```{r example2, eval = FALSE}
open_slides(cours = 01)
```

Loading the `tartine1` data.

```{r example3, eval = FALSE}
data(tartine1)
```
